Pillar 2 - Topic Modeling

### 2019-03-15 Pillar 2 - Topic Modeling.Rmd
control update

  burnin = 1000,
  iter   = 5000,
  thin   = 100

@@

### Manually
The function `my_cast_tdm` casts our dataframes into a tdm.
```{r my_cast_tdm, eval = TRUE}
my_cast_tdm <- function(data) data %>%
  count(`Course ID`, word) %>%
  cast_dtm(`Course ID`, word, n)

@@

```
####10-fold Cross-validation
NOT NEEDED TO BE FINISHED
```{r manual evaluation, cache = TRUE, eval = TRUE}
set.seed(1234)

#number of topics for trials
n_topic = seq(from = 2, to = 80, by = 2)

this_control <- list(

  nstart = 10,
  seed   = 1 : 10,
  best   = FALSE, #this is different

  burnin = 1000,
  iter   = 5000,
  thin   = 100

#
##cross-validate

#crossv_sets returns data.frame with 10-folds divided into train (DTM) and test sets(DTM)
crossv_sets <- function(dtm){
  #Setup
  n_documents <- nrow(dtm)
  folding <- sample(rep(1:10, ceiling(n_documents))[seq_len(n_documents)]) #not very elegant

  #functions
  create_trainset <- function(Fold){
    train_set = dtm[folding != Fold,]
  }

  create_testset <- function(Fold){
    test_set  = dtm[folding == Fold,]
  }

  #create folds
  folds <-  data.frame(Fold = 1:10) %>%
    mutate(train_set = map(Fold, .f = create_trainset),
           test_set  = map(Fold, .f = create_testset))
  return(folds)
}

cross_validate <- function(my_dtm){
  #Number of documents (D)
  D <- nrow(my_dtm)

  #Assign documents to a fold
  folding <- sample(rep(1:10, ceiling(D))[seq_len(D)])

  for(k in n_topics) {
    for(chain in 1:10){
      #Sets
      train_set <- my_dtm[folding != chain, ]
      test_set  <- my_dtm[folding == chain, ]

      #LDA
      training      <- LDA(train_set, k = k, control = my_control, method = "Gibbs")

      #best_training <- training@fitted[[which.max(logLik(training))]]
      return(perplexity(training, newdata = test_set))
      #testing  <- my_LDA(test_set, model = best_training, control = list())
    }
  }
}

#
##Create folds
###Find number of documents
D_overview <- nrow(d_cast$overview)
D_manual <- nrow(d_cast$manual)

###Assigning random numbers (1:10) to each row of our DTM
folding_overview <- sample(rep(seq_len(10), ceiling(D_overview))[seq_len(D_overview)])
folding_manual   <- sample(rep(seq_len(10), ceiling(D_manual))[seq_len(D_manual)])

for(k in n_topics){
  for(chain in 1:10){
    ###Divide into training and testing sets
      #overview
    training_set_overview <- d_cast$overview[folding!=chain,]
    test_set_overview     <- d_cast$overview[folding==chain,]
      #manual
    training_set_manual   <- d_cast$manual[folding!=chain,]
    test_set_manual       <- d_cast$manual[folding==chain,]

  }
}

```
## Fitting Model
From the results we see that the ideal number of topics is somewhere between 35 and 40. We train our models on 35 topics. Then we save them in the `Output`folder and in the ``Recommender System` folder.

```{r LDA fit, cache = TRUE, eval = TRUE}
topic_model <- tibble(

  n_topic = seq(from = 2, to = 80, by = 2)

>>>>

  burnin = 1000,
  iter   = 15000,
  thin   = 100

@@

```
From the results we see that the ideal number of topics is somewhere between 35 and 40.

## Fitting Model
The function `my_cast_tdm` casts our dataframes into a tdm.
```{r my_cast_tdm, eval = TRUE}
my_cast_tdm <- function(data) data %>%
  count(`Course ID`, word) %>%
  cast_dtm(`Course ID`, word, n)

@@

Next we train our model with different number of topics.
```{r LDA fit, cache = TRUE, eval = TRUE}
topic_model <- tibble(

  n_topic = seq(from = 2, to = 150, by = 2)
